\documentclass[a4paper, 10pt]{article}

% MARGIN AND PAGE LAYOUT
\usepackage[margin=1cm, top=1.0cm, bottom=0cm]{geometry}
\usepackage{parskip}

\usepackage{enumitem}
\setlist{nosep, leftmargin=*}
\usepackage{tabularx}

\usepackage{titlesec} % for customizing section titles
\usepackage{tabularx} % for making tables with fixed width columns
\usepackage{array} % tabularx requires this
\usepackage[dvipsnames]{xcolor} % for coloring text

\usepackage{enumitem} % for customizing lists
\usepackage{fontawesome5} % for using icons
\usepackage{amsmath} % for math
\usepackage[
    pdftitle={Saurabh Vishwakarma's CV},
    pdfauthor={Saurabh Vishwakarma},
    pdfcreator={Saurabh Vishwakarma},
    colorlinks=true,
    urlcolor=blue
]{hyperref} % for links, metadata and bookmarks
\usepackage[pscoord]{eso-pic} % for floating text on the page
\usepackage{calc} % for calculating lengths
\usepackage{bookmark} % for bookmarks
\usepackage{lastpage} % for getting the total number of pages
\usepackage{changepage} % for one column entries (adjustwidth environment)
\usepackage{paracol} % for two and three column entries
\usepackage{ifthen} % for conditional statements
\usepackage{needspace} % for avoiding page brake right after the section title
\usepackage{iftex} % check if engine is pdflatex, xetex or luatex
\usepackage{xcolor} % Include this in your preamble
\usepackage{fontspec}

% \setmainfont{Arial}[]

% \setmainfont{Times New Roman} % Change to any installed system font
\newcommand{\blue}[1]{\textcolor[HTML]{002855}{#1}}


% Ensure that generate pdf is machine readable/ATS parsable:
\ifPDFTeX
    \input{glyphtounicode}
    \pdfgentounicode=1
    % \usepackage[T1]{fontenc} % this breaks sb2nov
    \usepackage[utf8]{inputenc}
    \usepackage{lmodern}
\fi



% Some settings:
\AtBeginEnvironment{adjustwidth}{\partopsep0pt} % remove space before adjustwidth environment
\pagestyle{empty} % no header or footer
\setcounter{secnumdepth}{0} % no section numbering
\setlength{\parindent}{0pt} % no indentation
\setlength{\topskip}{0pt} % no top skip
\setlength{\columnsep}{0cm} % set column seperation
\makeatletter
\let\ps@customFooterStyle\ps@plain % Copy the plain style to customFooterStyle
\patchcmd{\ps@customFooterStyle}{\thepage}{
}{}{} % replace number by desired string
\makeatother
\pagestyle{customFooterStyle}

\titleformat{\section}{\needspace{4\baselineskip}\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule]

\setmainfont{Calibri}[
    Path=Calibri/, % Path to the folder containing Calibri font files
    Extension=.ttf,
    UprightFont=calibri,
    BoldFont=*-bold,
    % ItalicFont=calibri italic,
    % BoldItalicFont=calibri bold italic
]
\titlespacing{\section}{
    % left space:
    -1pt
}{
    % top space:
    0.3 cm
}{
    % bottom space:
    0.1 cm
} % section title spacing


\usepackage{enumitem}

\newlist{highlights}{itemize}{1}
% \setlist[highlights]{label=-, left=0pt, itemsep=0pt, topsep=0pt}

% \renewcommand\labelitemi{$\circ$} % custom bullet points

\newenvironment{highlightsforbulletentries}{
    \begin{itemize}[
        topsep=0.10 cm,
        parsep=0.10 cm,
        partopsep=0pt,
        itemsep=0pt,
        leftmargin=10pt
    ]
}{
    \end{itemize}
} % new environment for highlights for bullet entries


\newenvironment{onecolentry}{
    \begin{adjustwidth}{
       0 cm
    }{
        0 cm
    }
}{
    \end{adjustwidth}
} % new environment for one column entries





\newenvironment{header}{
    \setlength{\topsep}{0pt}\par\kern\topsep\centering\linespread{1.5}
}{
    \par\kern\topsep
} % new environment for the header


% save the original href command in a new command:
\let\hrefWithoutArrow\href

% new command for external links:
\renewcommand{\href}[2]{\hrefWithoutArrow{#1}{\ifthenelse{\equal{#2}{}}{ }{#2 }\raisebox{.15ex}{\footnotesize }}}


\begin{document}
    \newcommand{\AND}{\unskip
        \cleaders\copy\ANDbox\hskip\wd\ANDbox
        \ignorespaces
    }
    \newsavebox\ANDbox
    \sbox\ANDbox{}

% \textbf{\fontsize{18pt}{22pt}\selectfont \blue{Saurabh Vishwakarma}}
% \vspace{0.2cm}




\definecolor{blue}{HTML}{002855}


\begin{paracol}{2}
\begin{flushleft}
\textbf{\fontsize{26pt}{28pt}\selectfont \textcolor{blue}{Saurabh Vishwakarma}}\\[2pt]
\fontsize{16pt}{16pt}\selectfont Software Engineer
\end{flushleft}

\switchcolumn
\begin{flushright}
Gurugram Haryana \quad \href{tel:+91-7000729488}{+91 7000729488}\\
\href{mailto:contact@saurabhvishwakarma.in}{contact@saurabhvishwakarma.in}\\
\href{https://www.linkedin.com/in/saurabh254}{linkedin.com/in/saurabh254}\\
\href{https://github.com/saurabh254}{github.com/saurabh254} \quad
\href{https://saurabhvishwakarma.in}{saurabhvishwakarma.in}
\end{flushright}
\end{paracol}





\section{Professional Summary}
\vspace{0.1cm}

I'm a Software Engineer building scalable systems and improving performance for production applications. Focused on clean architecture, reliability, and maintainable code. Works across backend, data, and infrastructure with strong ownership and execution.

\section{Technical Skills}
\vspace{0.1cm}
\begin{itemize}
    \item \textbf{Frameworks:} FastAPI, SQLAlchemy, Django, React
    \item \textbf{Languages:} Python, GoLang, JavaScript
    \item \textbf{Database:} PostgreSQL, Supabase, Redis, MongoDB
    \item \textbf{Cloud \& Deployments:} AWS, Docker, Kubernetes, Linux, Terraform, Vercel
\end{itemize}

\section{Work Experience}
\vspace{0.3em}


\begin{onecolentry}
    \textbf{Software Engineer} \hfill October 2025 -  Present \\
    \blue{Synthlane} \hfill Gurugram, Haryana
    \begin{itemize}
% \item Built a \textbf{Customer Gateway layer} with \textbf{RBAC} using FastAPI to manage user operations and abstract internal orchestration workflows.
% \item Engineered deployments on \textbf{AWS ECS} using \textbf{Terraform} and \textbf{GitHub workflows}, making releases smoother and more reliable.
% \item Rebuilt broken internal tools on \textbf{Kubernetes} and added Grafana Alloy to improve reliability and monitoring
% \item Reduced FastAPI \textbf{p95} and\textbf{p99} latency from\textbf{ 450 ms} to under\textbf{ 120 ms} at \textbf{40 RPS} through deployment and application level performance optimizations.
\item Built a \textbf{FastAPI backend services} with \textbf{RBAC} to manage user operations and decouple internal orchestration workflows.
\item Designed authentication and authorization using \textbf{Okta} and \textbf{Supabase Auth} with \textbf{RBAC} and \textbf{RLS} for fine grained access control.
\item Integrated \textbf{Langfuse} for end-to-end tracing and observability across LLM and backend workflows.
\item Migrated data from \textbf{PostgreSQL} to \textbf{Supabase} using \textbf{Fivetran} and \textbf{dbt}, ensuring reliable data pipelines and transformations.
\item Automated deployments on \textbf{AWS ECS} using \textbf{Terraform} and \textbf{GitHub Actions}, improving release consistency and reliability.
\item Rebuilt internal tools on \textbf{Kubernetes} and integrated \textbf{Grafana Alloy} to strengthen system reliability and observability.
\item Reduced FastAPI \textbf{p95/p99 latency} from \textbf{450 ms} to \textbf{<100 ms} at \textbf{80 RPS} through application and infrastructure level optimizations.

\end{itemize}
\end{onecolentry}
\begin{onecolentry}
    \textbf{Software Engineer - Freelance} \hfill January 2025 - October 2025 \\
    \blue{Outlier AI} \hfill Remote
    \begin{itemize}
\item Developed a \textbf{Streamlit app} to compare AI model responses, incorporating performance metrics for 20+ models.
\item Enhanced LLM code generation through prompt design, curated datasets, and systematic evaluation, improving accuracy by 15\%.
\item Performed systematic A/B testing of prompt variations to improve model accuracy by 15\% across coding tasks.
\end{itemize}
\end{onecolentry}

\begin{onecolentry}
    \textbf{Software Engineer Intern} \hfill January 2024 -- January 2025 \\
    \blue{Hunkaar Labs} \hfill Bhopal, India
    \begin{itemize}
      \item Developed and deployed \textbf{FastAPI + Celery} microservices with an admin dashboard, serving \textbf{5,000+} users.
          \item Integrated Razorpay payments (\textbf{700+} transactions, \textbf{99\%} success) and added LangChain-based\textbf{ workflow automation}.
        \item Designed chat using \textbf{WebSockets}, \textbf{posts} and \textbf{stories} with REST APIs, and live streaming via \textbf{LiveKit}, achieving \textbf{99\%} uptime.
\end{itemize}
\end{onecolentry}

\section{Projects}

\vspace{0.2cm}
\noindent
\begin{tabularx}{\textwidth}{Xr}
\textbf{PinSphere}: Full-Stack Media Sharing Platform & 
\href{https://github.com/saurabh254/pinsphere}{GitHub Repository} \\
\end{tabularx}

\begin{itemize}
    \item Planned scalable architecture and \textbf{intelligent search} with Llama 3.2 \& Sbert, including \textbf{vector embeddings}.
    \item Optimized storage with \textbf{40\% compression} and enhanced image/video pipeline via Celery-based BlurHash processing.
    \item \textbf{Tech Stack:} FastAPI, React, PostgreSQL, MinIO, Celery, Large Language Models (LLMs), SBERT, AWS (S3, EC2)
\end{itemize}

\noindent
\begin{tabularx}{\textwidth}{Xr}
\textbf{RedisGo}: Redis implementation in GoLang  & 
\href{https://github.com/Saurabh254/redisgo}{GitHub Repository} \\
\end{tabularx}

\begin{itemize}
    \item Implements a TCP-based Redis-like server in Go (v2.1) using the \textbf{tidwall/resp }library, goroutines, channels, maps, and sync.RWMutex for concurrent key-value storage.

    \item Parses \textbf{RESP arrays} into typed commands (SET, GET, HELLO, client) and handles network I/O, connection lifecycle, and in-memory KV operations with minimal error handling.

    \item \textbf{Tech Stack:} Go, RESP Protocol, Goroutines, net
\end{itemize}



\section{Education}

\vspace{0.1cm}
\begin{tabularx}{\textwidth}{X r}
    \textbf{Bachelor of Technology in Computer Science Engineering} & \textit{July 2021–May 2025} \\
    \textit{NRI Institute of Information Science and Technology - Bhopal} & \\
\end{tabularx}
\begin{itemize}
    \item \textbf{Relevant Coursework:} Data Structures and Algorithms, DBMS, Operating Systems, Computer Networks, OOPs.
\end{itemize}



    
\section{Achievements}

\begin{onecolentry}
\begin{itemize}
    \vspace{0.1cm}
    \item Solved \textbf{300+} Data Structures and Algorithms problems on LeetCode, GeeksforGeeks, and Decoder.
    \item Contributed to open-source projects with bug fixes and feature enhancements for \textbf{3+} GitHub repositories.
    \item \textbf{Coding Profiles:} \href{https://codolio.com/profile/saurabh254}{Codolio}, 
          \href{https://www.geeksforgeeks.org/user/sauravvishwakarma030/}{GeeksforGeeks}, 
          \href{https://leetcode.com/u/saurabh254/}{LeetCode}, 
          \href{https://www.codechef.com/users/saurabh254}{CodeChef}, 
          \href{https://code.dcoder.tech/profile/sauravvishwakarma}{Dcoder}
\end{itemize}
\end{onecolentry}

\end{document}